Safe and Robust Formal Synthesis of Digital Controllers\\ for Continuous Plants

### 2018-04-17 automatica/paper.tex
nudge Fig 2

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=3cm] {
   \node[fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   \node[fill=gray!20] (verif) {{\sc Verify}};
   \&
   \node[ellipse,fill=gray!20] (done) {{\sc Done}}; 
    \\
  };

   \path
   ([yshift=2em]synth.east) edge node[align=center] {Candidate solution} ([yshift=2em]verif.west)
    ([yshift=-2em]verif.west) edge node[align=center] {Counter-example} ([yshift=-2em]synth.east)
    (verif) edge node {} (done);
 \end{tikzpicture}
}
 \caption{The CEGIS framework. \label{fig:CEGIS}}
\end{figure*}

>>>>

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=3.5cm] {
   \node[fill=gray!20,minimum height=1cm] (synth) {{\sc Synthesize}};
   \&
   \node[fill=gray!20,minimum height=1cm] (verif) {{\sc Verify}};
   \&
   \node[ellipse,fill=gray!20] (done) {{\sc Done}}; 
    \\
  };

   \path
   ([yshift=2em]synth.east) edge node[align=center] {Candidate solution} ([yshift=2em]verif.west)
    ([yshift=-2em]verif.west) edge node[align=center] {Counterexample} ([yshift=-2em]synth.east)
    (verif) edge node {} (done);
 \end{tikzpicture}
}
 \caption{The CEGIS framework\label{fig:CEGIS}}
\end{figure*}
